### 2024-08-08 NN/plots_latex.tex
zz

@@

@@

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/TanhFFNN-R2-vs-Num-of-Epochs-HiddenSize-12.png}
    \caption{TanhFFNN - R2 vs. Number of Epochs (Hidden Size: 12)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/TanhFFNN-R2-vs-Num-of-Epochs-HiddenSize-28.png}
    \caption{TanhFFNN - R2 vs. Number of Epochs (Hidden Size: 28)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/TanhFFNN-R2-vs-Num-of-Epochs-HiddenSize-20.png}
    \caption{TanhFFNN - R2 vs. Number of Epochs (Hidden Size: 20)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/TanhFFNN-R2-vs-Num-of-Epochs-HiddenSize-10.png}
    \caption{TanhFFNN - R2 vs. Number of Epochs (Hidden Size: 10)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/Relu2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-12.png}
    \caption{Relu2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 12)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/Relu2HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-20.png}
    \caption{Relu2HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 20)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/Relu1HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-10.png}
    \caption{Relu1HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 10)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/ReluFFNN-R2-vs-Num-of-Epochs-HiddenSize-10.png}
    \caption{ReluFFNN - R2 vs. Number of Epochs (Hidden Size: 10)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/ReluFFNN-R2-vs-Num-of-Epochs-HiddenSize-12.png}
    \caption{ReluFFNN - R2 vs. Number of Epochs (Hidden Size: 12)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/ReluFFNN-R2-vs-Num-of-Epochs-HiddenSize-28.png}
    \caption{ReluFFNN - R2 vs. Number of Epochs (Hidden Size: 28)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/ReluFFNN-R2-vs-Num-of-Epochs-HiddenSize-20.png}
    \caption{ReluFFNN - R2 vs. Number of Epochs (Hidden Size: 20)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/GRNN-R2-vs-Num-of-Epochs-HiddenSize-10.png}
    \caption{GRNN - R2 vs. Number of Epochs (Hidden Size: 10)}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/LinearFFNN-R2-vs-Num-of-Epochs-HiddenSize-28.png}
    \caption{LinearFFNN - R2 vs. Number of Epochs (Hidden Size: 28)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/LinearFFNN-R2-vs-Num-of-Epochs-HiddenSize-20.png}
    \caption{LinearFFNN - R2 vs. Number of Epochs (Hidden Size: 20)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/LinearFFNN-R2-vs-Num-of-Epochs-HiddenSize-12.png}
    \caption{LinearFFNN - R2 vs. Number of Epochs (Hidden Size: 12)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/LinearFFNN-R2-vs-Num-of-Epochs-HiddenSize-10.png}
    \caption{LinearFFNN - R2 vs. Number of Epochs (Hidden Size: 10)}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/Linear1HiddenLayer-R2-vs-Num-of-Epochs-HiddenSize-10.png}
    \caption{Linear1HiddenLayer - R2 vs. Number of Epochs (Hidden Size: 10)}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots/RBFN-R2-vs-Num-of-Epochs-HiddenSize-10.png}
    \caption{RBFN - R2 vs. Number of Epochs (Hidden Size: 10)}
\end{figure}

### 2024-08-08 NN/plots_preds_latex.tex
zz

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots_preds/R2-99.65-GRNN-Impedance module.png}
    \caption{Prediction of Impedance module with GRNN - R-Squared: 0.97}
\end{figure}

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots_preds/R2-99.23-TanhFFNN-Impedance-module.png}
    \caption{Prediction of Impedance module with TanhFFNN - R-Squared: 0.94}
\end{figure}
